Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-24 2019/NUMTA_Barkalov/Special Issure/article.tex
some minor corrections in references ans formulas

\documentclass[review]{elsarticle}

@@

	The first four steps of the algorithm repeat Step 1 -- Step 4 of the initial index algorithm from Section 3.
	Step 5. For each interval $(x_{i-1}, x_i), 1 \leq i \leq k+1$ 
\begin{flushleft}
	\begin{itemize}[\labelitemii]
		\item Compute the global characteristics $R_{glob}(i)$ according to formulae (\ref{R_1}), (\ref{R_2}), (\ref{R_3}) using the value $r_{\nu}=r_{\nu}^{glob}$
		\item Compute the local characteristics $R_{loc}(i)$ according to formulae (\ref{R_1}), (\ref{R_2}), (\ref{R_3}) using the value $r_{\nu}=r_{\nu}^{loc}$
		\item Determine the characteristic $R(i)$ as
\begin{equation}\label{R_max}
	R(i) = \max{\left\{ R_{glob}(i), \rho R_{loc}(i) \right\}}
\end{equation}
where $\rho=\Big(\frac{1-1/r_{M}^{glob}}{1-1/r_{M}^{loc}}\Big)^2$, if $\nu(x_{i-1})=\nu(x_i)=\nu$, and $\rho=1$, if $\nu(x_{i-1}) \neq \nu(x_i)$.
	\end{itemize}
\end{flushleft}

@@

	In Fig. \ref{fig:example_strongin}, the search domain (square) is shown, the feasible domain is highlighted by green, and the trial points generated by IA (a) and IA-DL (b) are marked. The best point is marked by red. For both methods, the evolvent with the parameter $m=10$ was used, the accuracy of the search for the solution $\epsilon=0.002$; the adaptive reserve parameter $\delta=0.008$ from (\ref{epsilon_nu}). For the IA method, the parameters $r_{\nu}=2.3, 1 \leq \nu \leq 4$ were used. The same values were used for the IA-DL method as the parameters $r_{\nu}^{glob}, 1 \leq \nu \leq 4$. Also, the parameters $r_{\nu}^{loc}=1.5, 1 \leq \nu \leq 4$ were used. To solve the problem with a predefined accuracy, 478 trials were required for the IA method compared to only 303 trials for the IA-DL method. The results of larger-scale numerical experiments are presented in Section 4.

	Let us formulate and prove the convergence conditions for the new algorithm IA-DL.\\
\textbf{Theorem 2}. Let us assume the index algorithm (IA) is applied to solve the problem (\ref{problem}) and for the values $r_{\nu}=r_{\nu}^{glob}, 1 \leq \nu \leq m+1$ the conditions of Theorem 1 are fulfilled. Then, the algorithm with dual estimate of the Lipschitz constants (IA-DL) with the parameters $r_{\nu}^{glob}>r_{\nu}^{loc}>1, 1\leq \nu \leq m+1$ when solving the same problem also generates a sequence of the trial points $\{y^k\}=\{y(x^k)\}$, any limit point $\bar{y}$ of which belongs to the set $Y_{\epsilon}$ from (\ref{Q_intervals}), i.e. satisfies the condition 
\begin{equation}\label{phi_bar_y}
	\varphi(\bar y) = \inf\left\{\varphi(y^k):g_j(y^k) \leq 0, 1 \leq j \leq m, k = 1,2,\ldots \right\} \leq \varphi(y_{\epsilon}).
\end{equation}
\textbf{Proof}.

	Because for the IA with the parameters $r_{\nu}=r_{\nu}^{glob}, 1 \leq \nu \leq m+1$ the conditions of Theorem 1 are fulfilled, then any limit point $\bar{y}=y(\bar{x})$ of the trial sequence generated by the IA for the problem (\ref{problem}) satisfies the conditions (\ref{phi_bar_y}).

>>>>

\documentclass[preprint]{elsarticle}

@@

	The first four steps of the algorithm repeat Step 1 -- Step 4 of the initial index algorithm from Section 3.
	Step 5. For each interval $(x_{i-1}, x_i), 1 \leq i \leq k+1,$ 
\begin{flushleft}
	\begin{itemize}[\labelitemii]
		\item Compute the global characteristics $R_{glob}(i)$ according to formulae (\ref{R_1}), (\ref{R_2}), (\ref{R_3}) using the value $r_{\nu}=r_{\nu}^{glob}$
		\item Compute the local characteristics $R_{loc}(i)$ according to formulae (\ref{R_1}), (\ref{R_2}), (\ref{R_3}) using the value $r_{\nu}=r_{\nu}^{loc}$
		\item Determine the characteristic $R(i)$ as
\begin{equation}\label{R_max}
	R(i) = \max{\left\{ R_{glob}(i), \rho R_{loc}(i) \right\}}
\end{equation}
where $\rho=\Big(\frac{1-1/r_{M}^{glob}}{1-1/r_{M}^{loc}}\Big)^2$, if $\nu(x_{i-1})=\nu(x_i)=\nu$, and $\rho=1$, if $\nu(x_{i-1}) \neq \nu(x_i)$.
	\end{itemize}
\end{flushleft}

@@

	In Fig. \ref{fig:example_strongin}, the search domain (square) is shown, the feasible domain is highlighted by green, and the trial points generated by IA (a) and IA-DL (b) are marked. The best point is marked by red. For both methods, the evolvent with the parameter $m=10$ was used, the accuracy of the search for the solution $\epsilon=0.002$; the adaptive reserve parameter $\delta=0.008$ from (\ref{epsilon_nu}). For the IA method, the parameters $r_{\nu}=2.3, 1 \leq \nu \leq 4$ were used. The same values were used for the IA-DL method as the parameters $r_{\nu}^{glob}, 1 \leq \nu \leq 4$. Also, the parameters $r_{\nu}^{loc}=1.5, 1 \leq \nu \leq 4,$ were used. To solve the problem with a predefined accuracy, 478 trials were required for the IA method compared to only 303 trials for the IA-DL method. The results of larger-scale numerical experiments are presented in Section 4.

	Let us formulate and prove the convergence conditions for the new algorithm IA-DL.\\
\textbf{Theorem 2}. Let us assume the index algorithm (IA) is applied to solve the problem (\ref{problem}) and for the values $r_{\nu}=r_{\nu}^{glob}, 1 \leq \nu \leq m+1$ the conditions of Theorem 1 are fulfilled. Then, the algorithm with dual estimate of the Lipschitz constants (IA-DL) with the parameters $r_{\nu}^{glob}>r_{\nu}^{loc}>1, 1\leq \nu \leq m+1,$ when solving the same problem also generates a sequence of the trial points $\{y^k\}=\{y(x^k)\}$, any limit point $\bar{y}$ of which belongs to the set $Y_{\epsilon}$ from (\ref{Q_intervals}), i.e. satisfies the condition 
\begin{equation}\label{phi_bar_y}
	\varphi(\bar y) = \inf\left\{\varphi(y^k):g_j(y^k) \leq 0, 1 \leq j \leq m, k = 1,2,\ldots \right\} \leq \varphi(y_{\epsilon}).
\end{equation}

\textbf{Proof}. Because for the IA with the parameters $r_{\nu}=r_{\nu}^{glob}, 1 \leq \nu \leq m+1,$ the conditions of Theorem 1 are fulfilled, then any limit point $\bar{y}=y(\bar{x})$ of the trial sequence generated by the IA for the problem (\ref{problem}) satisfies the conditions (\ref{phi_bar_y}).
